Aggregated Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2017-10-23 aggregation/agg-agg.tex
Private disclosure work

\subsubsection{Complete Foreground}

See Figure~\ref{fig:aggregation}b.  A foreground can be viewed as a linked set of unit processes.  The collection of processes themselves make up the foreground of the study, and so exchanges among them are recorded in $A_f$, and exchanges outside the foreground are represented in $A_d$ or $B_f$.  A complete foreground represents the full disclosure of a model, and a reader can replicate and extend it independently.  Any co-production treatment, such as an allocation or system expansion, can only be fully expressed as a foreground model, because it intrinsically involves a collection of linked unit processes.

>>>>

\subsubsection{Foreground or Foreground Fragment}

See Figure~\ref{fig:aggregation}b.  A foreground can be viewed as a linked set of unit processes.  The collection of processes themselves make up the foreground of the study, and so exchanges among them are recorded in $A_f$, and exchanges outside the foreground are represented in $A_d$ or $B_f$.  A complete foreground represents
the full disclosure of a model, and a reader can replicate and extend it independently.  A fragment of the PSM can also be published as a complete foreground. Any co-production treatment, such as an allocation or system expansion, can only be fully expressed as a foreground fragment, because it intrinsically involves a collection of linked unit processes.
